\chapter{Acknowledgments}\label{sec:acknowledgments}

Here we acknowledge those people and organisations the assisted in the development of this and previous releases of the SBGN \AFl specification. First we specifically acknowledge those who contributed directly to each revision of the  specification document, followed by a comprehensive acknowledgement of contributors that attended workshops and forum meetings or in some other way provided input to the standard. Finally, we acknowledge the bodies that provided financial support for the development of the standard.


 We aim this list to be rather complete. We are very sorry if we forgot someone, and will be grateful if you notified us of any omission.

\section{Level 1 Release 1.0}

The specification was written by Huaiyu Mi, Falk Schreiber, Nicolas Le Nov\`{e}re, Stuart Moodie, Anatoly Sorokin, Michael Hucka, Emek Demir, Yukiko Matsuoka, Katja Wegner and Hiroaki Kitano. In addition, the specification benefited much from the help of Frank Bergmann, Sarala Dissanayake and Paul Thomas.

\section{Level 1 Release 1.1}
The specification of \AF Level 1 Release 1.1 was written by Huaiyu Mi, with significant contributions from Falk Schreiber and Stuart Moodie.  Other contributors include (in alphabetic order) Tobias Czauderna, Emek Demir, Nicolas Le Nov\`{e}re, Yukiko Matsuoka, Anatoly Sorokin, Alice Vill\'{e}ger and Katja Wegner.

\section{Level 1 Release 1.2}
The specification of \AF Level 1 Release 1.2 was written by Huaiyu Mi, with significant contributions from Falk Schreiber, Stuart Moodie, Tobias Czauderna and Anatoly Sorokin.  Other contributors include (in alphabetic order) Michael Blinov, Emek Demir, Robin Haw, Anushya Muruganujan, Nicolas Le Nov\`{e}re, Augustin Luna, Paul Thomas and Katja Wegner.

\section{Comprehensive list of acknowledgements}

Here is a more comprehensive list of people who have been actively involved in SBGN development, either by their help designing the languages, their comments on the specification, help with development infrastructure or any other useful input.  We aim this list to be rather complete. We are very sorry if we forgot someone, and will be grateful if you notify us of any omission.

Mirit Aladjem, Frank Bergmann, Michael Blinov, Bernard de Bono, Sarah Boyd, Laurence Calzone, Melanie Courtot, David Croft, Tobias Czauderna, Emek Demir, Johannes W. Dietrich, Ugur Dogrusoz, Damien Fleury, Tom Freeman, Akira Funahashi, Ralph Gauges, Peter Ghazal, Samik Ghosh, Igor Goryanin, Anja Hartmann, Robin Haw, Michael Hucka, Matthias Jeschke, Mathias John, Akiya Jouraku, Astrid Junker, Hideya Kawaji, Douglas Kell, Sohyoung Kim, Hiroaki Kitano, Christian Klukas, Kurt Kohn, Fedor Kolpakov, Nicolas Le Nov\`{e}re, Lu Li, Augustin Luna, Yukiko Matsuoka, Carsten Maus, Alexander Mazein, Huaiyu Mi, Stuart Moodie, Ulrike M\"unzner, Anushya Muruganujan, Michael Pedersen, Jacqueline Quinn, Stefan Rybacki, Sven Sahle, Chris Sander, Herbert Sauro, Esther Schmidt, Falk Schreiber, Jacky Snoep, Anatoly Sorokin, Jessica Stephens, Linda Taddeo, Carolyn Talcott, Lin Uhrmacher, Martijn van Iersel, Alice Vill\'{e}ger, Steven Watterson, Katja Wegner (Wengler), Sarala Wimalaratne (Dissanayake), Guanming Wu, R\"obbe W\"unschiers.

The authors are also grateful to all the attendees of the SBGN meetings, as well as to the subscribers of the \mailto{sbgn-discuss@sbgn.org} mailing list.

\section{Financial Support}

The development of SBGN was mainly supported by a grant from the Japanese New Energy and Industrial Technology Development Organization (NEDO, \url{http://www.nedo.go.jp/}). 
The Okinawa Institute of Science and Technology (OIST, \url{http://www.oist.jp/}), 
the AIST Computational Biology Research Center (AIST CBRC, \url{http://www.cbrc.jp/index.eng.html}), 
the British Biotechnology and Biological Sciences Research Council (BBSRC, \url{http://www.bbsrc.ac.uk/}) through a Japan Partnering Award, 
the European Media Laboratory (EML Research gGmbH, \url{http://www.eml.org/english/}), 
the Beckman Institute at the California Institute of Technology (\url{http://bnmc.caltech.edu}), 
Ontario Institute for Cancer Research (OICR, \url{http://oicr.on.ca/}), 
Ontario Genomics Institute (OGI, \url{http://www.ontariogenomics.ca/}), 
National Science Foundation (NSF, \url{http://www.nsf.gov/}), 
USC Norris Comprehensive Cancer Center (\url{http://uscnorriscancer.usc.edu/}), 
Martin Luther University Halle-Wittenberg (\url{http://www.uni-halle.de/}), 
Monash University (\url{http://www.monash.edu.au/}), 
IPK Gatersleben (\url{http://www.ipk-gatersleben.de/en/}), 
University of Rostock (\url{http://www.uni-rostock.de/})  and 
German Federal Ministry of Research and Education (\url{http://www.bmbf.de/}) provided additional support for SBGN workshops. 
Some help was provided by the Japan Science and Technology Agency (JST, \url{http://www.jst.go.jp/}) and the Genome Network Project of the Japanese Ministry of Education, Sports, Culture, Science, and Technology (MEXT, \url{http://www.mext.go.jp/}) for the development of the gene regulation network aspect of SBGN, and from the Engineering and Physical Sciences Research Council (EPSRC, \url{http://www.epsrc.ac.uk}) during the redaction of the specification.

%The development of SBGN was mainly supported by a grant from the Japanese \emph{New Energy and Industrial Technology Development Organization} (NEDO, \url{http://www.nedo.go.jp/}). The \emph{Okinawa Institute of Science and Technology} (OIST, \url{http://www.oist.jp/}), the \emph{AIST Computational Biology Research Center} (AIST CBRC, \url{http://www.cbrc.jp/index.eng.html}) the British \emph{Biotechnology and Biological Sciences Research Council} (BBSRC, \url{http://www.bbsrc.ac.uk/}) through a Japan Partnering Award, the European Media Laboratory (EML Research gGmbH, \url{http://www.eml.org/}), the Beckman Institute at the California Institute of Technology (\url{http://bnmc.caltech.edu}), the IPK Catersleben (\url{http://www.ipk-gatersleben.de}) and the National Science Foundation (\url{http://www.nsf.gov/}) provided additional support for SBGN workshops.  Some help was provided by the \emph{Japan Science and Technology Agency} (JST, \url{http://www.jst.go.jp/}) and the \emph{Genome Network Project} of the Japanese Ministry of Education, Sports, Culture, Science, and Technology (MEXT, \url{http://www.mext.go.jp/}) for the development of the gene regulation network aspect of SBGN, and from the \emph{Engineering and Physical Sciences Research Council} (EPSRC, \url{http://www.epsrc.ac.uk}) during the redaction of the specification.