\section{Semantic rules}

\subsection{Namespaces}

The notation has a concept of a namespace within which entities with the same
identifying attributes are regarded as identical. The SBGN namespaces are shown
in table \ref{tab:namespacedefs}.

\begin{center}
\tablecaption{Namespace scope definitions.}
\label{tab:namespacedefs}
\begin{small}
\tablefirsthead{\hline
  Namespace Scope & Entities affected & Notes\\\hline}
\tablehead{\hline
\multicolumn{3}{|l|}{\small\sl continued from previous page}\\
\hline\hline
  Namespace scope & Entities Effected & Notes\\\hline\hline}
\tabletail{\hline
\multicolumn{3}{|r|}{\small\sl continued on next page}\\
\hline}
\tablelasttail{\hline}
\begin{supertabular}{|l|p{5cm}|p{5cm}|}\hline
%
MapDiagram & CompartmentNode, SubMapDiagram, EquivalenceNode & \\\hline
%
CompartmentShape & BasicEntityNode & If no \glyph{compartment} is drawn then all BasicEntityNodes are assumed to belong to an invisible ``default'' compartment.\\\hline
EntityType & StateVariable, Annotation & \\\hline
ComplexType & EntityType & \\\hline
\end{supertabular}
\end{small}
\end{center}

\subsection{Compartment spanning}

In all cases an AFN cannot \emph{belong} to more than one
compartment. However, an AFN can be \emph{drawn} over more than one
compartment. In such cases the decision on which is the owning
compartment is deferred to the drawing tool or the
author. ComplexNodes may contain AFNs which belong to different
compartments and in this way a complex can be used to describe an
entity that spans more than one compartment.

This restriction makes it impossible to represent in a semantically
correct way a macromolecule that spans more then one compartment ---
for example a receptor protein. It is clearly desirable to be able to
show a macromolecule in a manner that the biologist expects (\ie
spanning from the outside through the membrane to the
inside). Therefore, the author is recommended to draw the
macromolecule across compartment boundaries, but the underlying SBGN
semantic model will assign it to only one. The assignment to a
compartment may be decided by the software drawing tool or the
author. Note that this has implications for auto-layout algorithms as
they will only be able to treat such entity nodes as contained within
a compartment and will have no way of knowing a macromolecule spans a
compartment.

The current solution is consistent with other Systems Biology
representations such as SBML and BioPAX. For more information about the
problems representing membrane spanning proteins and the rationale
behind the current solution see \sect{sec:postponed}.

\subsection{Compartments}

The layout of compartments in an SBGN diagram does not imply anything
about the topology of compartments in the cell. Compartments should be
bounded and may overlap. However, adjacency and the nesting of
compartments does not imply that these compartments are next to each
other physically or hat one compartment contains the other.

\subsection{Modulation}

It is implied, but not defined explicitly that a process has a rate at
which it converts its input AFNs to its output AFNs. This concept is
important in understanding how SBGN describes process modulation.

\begin{enumerate}
\item A process with no modulations has an underlying ``basal rate''
  which describes the rate at which it converts inputs to outputs.
\item Modulation changes the basal rate in an unspecified fashion.
\item Stimulation is a modulation that's effect is to increase the basal rate.
\item Inhibition is a modulation that's effect is to decrease the basal rate.
\item The above types of modulation, when assigned to the same process are combined and have a multiplicative effect on the basal rate of the process.
\item Modulators that do not interact with each other in the above manner should be drawn as modulating different process nodes. Their effect is therefore additive.
\item At most one trigger can be assigned to a process. Two triggers
  would imply an implicit Boolean AND or OR operator. For clarity only
  one trigger can be assigned to a process and such combinations must be
  explicitly expressed as the Boolean operators.
\item At most one catalysis can be assigned to a process. A catalysis
  modulation implies that the exact biochemical mechanism underlying
  the process is known. In this context two catalysis reactions cannot
  be assigned to the same process as they are
  independent reactions. Other AFNs that modulate the catalysis can be
  assigned to the same process as modulators, stimulators, and
  inhibitors and will have a multiplicative modulation on the reaction
  rate defined by the catalysis.
\end{enumerate}

\subsection{Submaps}

Submaps are a visual device that allow a map to be split into several
views. They remain, however, part of the main map and share its
namespace. As a test of validity it should be possible to reintroduced
a submap into the main map by eliminating the SubMapNode and merging
the equivalent EntityPoolNodes in both maps.

\subsubsection{Rules for mapping to submaps}

An ActivityFlowNode in the main map can be mapped to one in the submap
using a TagNode in the submap and SubMapTerminals (see \sect{submap}) in the main map. For a
mapping between map and submap to exists the following must be true:

\begin{enumerate}
\item The identifiers in the TagNode and SubMapTerminals must be identical.
\item The AFNs must be identical.
\end{enumerate}

\subsubsection{Requirement to define a mapping}

If a map and submap both contain the same AFN, then a
mapping between them must be defined as above.
