\chapter{Acknowledgments}\label{sec:acknowledgments}

Here we acknowledge those people and organisations the assisted in the development of this and previous releases of the SBGN \AFl specification. First we specifically acknowledge those who contributed directly to each revision of the  specification document, followed by a comprehensive acknowledgement of contributors that attended workshops and forum meetings or in some other way provided input to the standard. Finally, we acknowledge the bodies that provided financial support for the development of the standard.


 We aim this list to be rather complete. We are very sorry if we forgot someone, and will be grateful if you notified us of any omission.

\section{Level 1 Release 1.0}

The specification was written by Huaiyu Mi, Falk Schreiber, Nicolas Le Nov\`{e}re, Stuart Moodie, Anatoly Sorokin, Michael Hucka, Emek Demir, Yukiko Matsuoka, Katja Wegner and Hiroaki Kitano. In addition, the specification benefited much from the help of Frank Bergmann, Sarala Dissanayake and Paul Thomas.

\section{Level 1 Release 1.1}
The specification of \AF Level 1 Release 1.1 was written by Huaiyu Mi, with significant contributions from Falk Schreiber and Stuart Moodie.  Other contributors include (in alphabetic order) Tobias Czauderna, Emek Demir, Nicolas Le Nov\`{e}re, Yukiko Matsuoka, Anatoly Sorokin, Alice Vell\'{e}ger, Katja Wegner.

\section{Level 1.1 Release 1.2}
The specification of \AF Level 1 Release 1.1 was written by Huaiyu Mi, with significant contributions from Falk Schreiber and Stuart Moodie, Tobias Czauderna and Anatoly Sorokin.  Other contributors include (in alphabetic order) Michael Blinov, Emek Demir, Robin Haw, Anushya Muruganujan, Nicolas Le Nov\`{e}re, Augustin Luna, Paul Thomas, Katja Wegner, .

\section{Comprehensive list of achnowledgements}

Here is a more comprehensive list of people who have been actively involved in SBGN development, either by their help designing the languages, their comments on the specification, help with development infrastructure or any other useful input.  We aim this list to be rather complete. We are very sorry if we forgot someone, and will be grateful if you notify us of any omission.

Mirit Aladjemm, Frank Bergmann, Sarah Boyd, Laurence Calzone, Tobias Czauderna, Melanie Courtot, Emek Demir, Ugur Dogrusoz, Tom Freeman, Akira Funahashi, Ralph
Gauges, Peter Ghazal, Samik Ghosh, Igor Goryanin, Michael Hucka, Akiya Jouraku, Hideya Kawaji, Douglas Kell, Sohyoung Kim, Hiroaki Kitano, Kurt
Kohn, Fedor Kolpakov, Nicolas Le Nov\`{e}re, Lu Li, Augustin Luna, Yukiko Matsuoka, Huaiyu Mi, Stuart Moodie, Sven Sahle, Chris Sander, Herbert
Sauro, Esther Schmidt, Falk Schreiber, Jacky Snoep, Anatoly Sorokin, Jessica Stephens, Linda Taddeo, Paul, Thomas, Steven Watterson, Alice Vill\'{e}ger, Katja
Wegner, Sarala Wimalaratne, Guanming Wu.

The authors are also grateful to all the attendees of the SBGN meetings, as well as to the subscribers of the \mailto{sbgn-discuss@sbgn.org} mailing list.

\section{Financial Support}

The development of SBGN was mainly supported by a grant from the Japanese \emph{New Energy and Industrial Technology Development Organization} (NEDO, \url{http://www.nedo.go.jp/}).  The \emph{Okinawa Institute of Science and Technology} (OIST, \url{http://www.oist.jp/}), the \emph{AIST Computational Biology Research Center} (AIST CBRC, \url{http://www.cbrc.jp/index.eng.html}) the British \emph{Biotechnology and Biological Sciences Research Council} (BBSRC, \url{http://www.bbsrc.ac.uk/}) through a Japan Partnering Award, the European Media Laboratory (EML Research gGmbH, \url{http://www.eml-r.org/}), the Beckman Institute at the California Institute of Technology (\url{http://bnmc.caltech.edu}) and the IPK Catersleben (\url{(http://www.ipk-gatersleben.de}) provided additional support for SBGN workshops.  Some help was provided by the \emph{Japan Science and Technology Agency} (JST, \url{http://www.jst.go.jp/}) and the \emph{Genome Network Project} of the Japanese Ministry of Education, Sports, Culture, Science, and Technology (MEXT, \url{http://www.mext.go.jp/}) for the development of the gene regulation network aspect of SBGN, and from the \emph{Engineering and Physical Sciences Research Council} (EPSRC, \url{http://www.epsrc.ac.uk}) during the redaction of the specification.