\chapter{Activity Flow glyphs}
\label{chp:af:glyphs}

\section{Overview}
\label{sec:af:overview}
\input{af_overview.tex}

\section{Controlled vocabularies used in \SBGNAFLone}\label{af:sec:CVs}

\input{CVs.tex}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%                   Activity nodes
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Activity nodes}\label{sec:af:ANs}

An \emph{Activity node} (AN) represents the activity of an entity or an entity pool, but not the entities themselves. For instance, multiple activity nodes can be used to represent different activities of a particular entity, while one activity node can be used to represent the activity of a complex multimer. In addition to activities of material entities, \SBGNAFLone represents activity from a conceptual entity: \emph{phenotype}.  Auxiliary units, such as \emph{units of information}, can be used to indicate the material property of the activity source.  Each activity is displayed only once in a particular compartment.


\input{biological_Activity.tex}
%\input{process.tex}
\input{phenotype.tex}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%                   Auxiliary units
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Auxiliary units}\label{sec:af:AUs}

\input{unit_information.tex}
\input{submap_terminal.tex}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%                   Container nodes
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Glyph: Compartment}
\label{sec:compartment}

\input{compartment.tex}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%                  Arcs
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Influence arcs}\label{sec:af:arcs}

Influence arcs represent direct or indirect influences of biological activities on other activities. \SBGNAFLone provides four influence arcs: \glyph{positive influence}, \glyph{negative influence}, \glyph{unknown influence} and  \glyph{necessary stimulation}.

\input{positive_infl.tex}
\input{negative_infl.tex}
\input{unknown_infl.tex}
\input{necessary_stim.tex}



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%                   Logical operators
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Logical operator nodes}\label{sec:af:logic}
The logical operators \glyph{and}, \glyph{or} and \glyph{not} perform a Boolean operation to give a binary output. An \AF map can represent a dynamic model in which activity nodes are considered to have states. Activity above a certain threshold is treated as True and activity below this threshold is treated as False. The \glyph{delay} glyph is currently categorised as a logical operator because it uses \glyph{logic arcs} for its connections, although it does not perform a logical operation.
\input{and.tex}
\input{or.tex}
\input{not.tex}
\input{delay.tex} 

\section{Logic arc}
\label{sec:af:logic_arc}
\input{logic_arc.tex}

\section{Annotating nodes and arcs}
\input{annotation.tex}

\section{Referring to other nodes}
\label{sec:ref_nodes}



\input{tag.tex}
\input{equivalence_arc.tex}

\section{Glyph: Submap}
\label{sec:submap}
\input{submap.tex}

