\chapter{Revision History}

\section{Version 1.0 to Version 1.1}

There are three major changes in glyphs in Version 1.1 of the \SBGNAFLone specification. 
\begin{enumerate}
\item{Add \emph{unit of information} to the compartment.  This is done in accordance with \SBGNPDLone specification.}
\item{Remove \emph{perturbation} from the activity node, and add it to the \emph{unit of information} to decorate a \emph{biological activity} node.  The change was based on a survey conducted in August 2011.
}
\item{Add \emph{process} as an activity node. This is rather controversial at the beginning.  The issue was to make a process both an origin and a target of arcs.  It was not possible in AF V. 1.0 because a \emph{phenotype} cannot be the origin of an arc.  The details of this issue and subsequent survey (August 2011) are described on the SBGN website. The survey did not yield a concrete solution.  Through an additional discussion on the SBGN discussion list, this seems to be the best solution for the purpose without violating semantic rules.
}
\end{enumerate}

\textit{Version 1.1 was never officially released due to some disagreements in the change, especially in the use of process. It served as a working draft only.}

\section{Version 1.1 to Version 1.2}

Below are the changes incorporated into Version 1.2 of the \SBGNAFLone specification.

\begin{center}
%\tablecaption{Namespace scope definitions.}
\label{tab:revision history}
\tablefirsthead{\hline
Description & Tracker ID\\\hline}
\tablehead{\hline
\multicolumn{2}{|l|}{\small\sl continued from previous page}\\
\hline\hline
Description & Tracker ID\\\hline\hline}
\tabletail{\hline
\multicolumn{2}{|r|}{\small\sl continued on next page}\\
\hline}
\tablelasttail{\hline}
\begin{supertabular}{|p{12cm}|c|}\hline
Add \emph{Unit of information for Compartment}, section \ref{sec:af:unitInfoComp} & \\\hline
Add \emph{Unit of information for Compartment} to the ref card (Appendix \ref{sec:refcard}) & \\\hline
Remove \emph{perturbation} from Activity node section (\ref{sec:af:ANs}) & \\\hline
Add \emph{perturbation} to the unit of information section (\ref{sec:af:unitInfo}) & \\\hline
Modify \emph{perturbation} glyph in figures 2.1, 2.5, 2.17, A.4 and refcard accordingly (Appendix \ref{sec:refcard}). & \\\hline
Add \emph{process} to the Activity node section (\ref{sec:af:ANs})  & \\\hline
Modify figure A4 by adding the \emph{process} glyph.  & \\\hline
Modify the description for \emph{biological activity} in section 2.3.1 to clarify that it is for molecular activity, so to differentiate it from the activities from \emph{process}.  & \\\hline
Modify the description for \emph{phenotype} in section 2.3.3.  & \\\hline
Modify tables in section 3.3.1 and 3.3.2 
- Remove \emph{perturbation} 
- Add \emph{process} & \\\hline

Add \emph{phenotype} as input for \emph{equivalent arc} in section 3.3.1 & \\\hline
Remove the sentence "If an activity has participants in at least two different compartments, the activity node has to be either in a compartment where the activity has at least one participant or in the empty space." in section 4.2.1.8 & \\\hline
In section 4.2.1.8, change the first sentence "If an activity has all participants ..." to "If a network has all participants...." & \\\hline
In section 4.2.1.8, add a sentence "Edges/arcs are allowed to cross the compartment boundaries when the input and output ANs are in two different compartments." & \\\hline
Add \emph{delay} in the line of Logical operators in Table 2.1 & \\\hline
Correct figure legend for Figure 2.10.  The example on the right side shows an incorrect representation. & \\\hline
In section 2.2, controlled vocabularies, clarify that the terms are to describe the unit of information of the ANs &
\\\hline
Rewrite figure legends with more details throughout section 2 &
\\\hline
Modify Figure A3 in Appendix A (TGF beta signaling pathway) by changing the \emph{Gene transcription} phenotype node to a biological activity node.  However, it should be discussed whether phenotype can be an input or not. & 2992312 \\\hline
Update SBO term (SBO:0000255 to SBO:0000002) in section 2.2.3  & 3068940 \\\hline
\end{supertabular}
\end{center}

\section{Version 1.2 to Version 1.3}

Below are the changes incorporated into Version 1.3 of the \SBGNAFLone specification.

\begin{center}
%\tablecaption{Namespace scope definitions.}
\label{tab:revision history}
\tablefirsthead{\hline
Description & Tracker ID\\\hline}
\tablehead{\hline
\multicolumn{2}{|l|}{\small\sl continued from previous page}\\
\hline\hline
Description & Tracker ID\\\hline\hline}
\tabletail{\hline
\multicolumn{2}{|r|}{\small\sl continued on next page}\\
\hline}
\tablelasttail{\hline}
\begin{supertabular}{|p{11.5cm}|c|}\hline
Added Section \ref{sec:notes} about the typographical conventions and requirement levels and moved requirement levels in Section \ref{sec:af:layout-intro} to Section \ref{sec:notes} to make these levels valid throughout the document
& \href{https://github.com/sbgn/activity-flow/issues/5}{\#5} \\\hline
Updated the document to accurately reflect the requirement levels (must vs should)
& \href{https://github.com/sbgn/activity-flow/issues/6}{\#6} \\\hline
Moved first paragraph of Chapter \ref{chp:af:glyphs} that explains the structure of the document to Section \ref{sec:structure} of Chapter \ref{sec:intro} 
& \href{https://github.com/sbgn/activity-flow/issues/7}{\#7} \\\hline
Added sections for \glyph{tag} and \glyph{submap terminal} glyphs (Section \ref{sec:tag} and \ref{sec:submapTerminal}, respectively) 
& \href{https://github.com/sbgn/activity-flow/issues/8}{\#8} \href{https://github.com/sbgn/activity-flow/issues/9}{\#9}\\\hline
Reorganised the document structure to make it compatible with PD Spec L1V2.1
& \href{https://github.com/sbgn/activity-flow/issues/10}{\#10} \href{https://github.com/sbgn/activity-flow/issues/23}{\#23}\\\hline
Reviewed all figures and the reference card and made improvements and corrections.  
& \href{https://github.com/sbgn/activity-flow/issues/11}{\#11} \href{https://github.com/sbgn/activity-flow/issues/12}{\#12} \href{https://github.com/sbgn/activity-flow/issues/16}{\#16}\\\hline
Changed section titles ``Syntax" $\rightarrow$ ``Connectivity and containment" and ``Semantic rules" $\rightarrow$ ``Glyph specific rules" to remove the syntactic and semantic distinction in the rules  
& \href{https://github.com/sbgn/activity-flow/issues/10}{\#10} \\\hline
Updated containment table in Section \ref{sec:containment} to indicate containment of compartments by other compartments, also added submap column and submap terminal row  
& \href{https://github.com/sbgn/activity-flow/issues/15}{\#15} \\\hline
Fixed the broken hyperlinks throughout the document 
& \href{https://github.com/sbgn/activity-flow/issues/18}{\#18} \\\hline
Added new row for Biological activity and LO abbreviation to Logical operators row in Section \ref{sec:af:overview} 
& \href{https://github.com/sbgn/activity-flow/issues/22}{\#22} \\\hline
Updated the format used in sections for logical operator glyphs to match the PD Spec L1V1.2. Updated logical operator definitions and added examples to \glyph{and}, \glyph{not} and \glyph{delay} glyphs
& \href{https://github.com/sbgn/activity-flow/issues/13}{\#13} \href{https://github.com/sbgn/activity-flow/issues/35}{\#35} \href{https://github.com/sbgn/activity-flow/issues/36}{\#36} \\\hline
Added example for glyph \glyph{unknown influence} in Section \ref{sec:af:unknown_infl}
& \href{https://github.com/sbgn/activity-flow/issues/12}{\#12}  \\\hline
Updated node connectivity table in Section \ref{sec:node-connectivity} to fix some connections
& \href{https://github.com/sbgn/activity-flow/issues/14}{\#14} \\\hline
Changed notation to use \textit{Origin} and \textit{Target} in glyph explanations and used \textit{Source (S)} and \textit{Target (T)} in node connectivity table 
& \href{https://github.com/sbgn/activity-flow/issues/19}{\#19} \\\hline
Added missing subsections to Section \ref{sec:af:biologicalActivity}, \ref{sec:af:phenotype}, \ref{sec:compartment}, \ref{sec:annotation} and \ref{sec:submap}
& \href{https://github.com/sbgn/activity-flow/issues/24}{\#24} \\\hline
Changed Section \ref{sec:af:unitInfo} title from ``Glyph: Unit of information for Biological activity" to ``Glyphs: Units of information for Biological activity". Also changed naming of units of information (e.g., unit of information of a macromolecule to macromolecule unit of information) together with Figure \ref{fig:af:unitInfo}
& \href{https://github.com/sbgn/activity-flow/issues/29}{\#29} \\\hline
Refined definitions of \glyph{positive influence}, \glyph{negative influence} and \glyph{necessary stimulation} glyphs in Section \ref{sec:af:positive_infl}, \ref{sec:af:negative_infl} and \ref{sec:af:necessary_stim}
& \href{https://github.com/sbgn/activity-flow/issues/31}{\#31} \href{https://github.com/sbgn/activity-flow/issues/33}{\#33} \href{https://github.com/sbgn/activity-flow/issues/34}{\#34} \\\hline
Section 2.5 ``Container nodes" is replaced by subsection 2.5.1 ``Glyph: Compartment" and now Section 2.5 is ``Glyph: Compartment".
& \href{https://github.com/sbgn/activity-flow/issues/30}{\#30} \\\hline
Renamed all occurrences of ``modulations" to ``influences" including section title 2.8 Modulation arcs (in L1V1.2) \(\rightarrow\) 2.6 Influence arcs (in L1V1.3) 
& \href{https://github.com/sbgn/activity-flow/issues/27}{\#27} \\\hline
Fixed typos and modified visual style of some tables/figures throughout the document
& \\\hline
\end{supertabular}
\end{center}